### 2018-03-07 paper/implementations.tex
Start working on the implementation.tex file

>>>>

In the previous sections we've discussed the types of build system in text, but the way we came to our conclusions was by developing a framework to fit the builds in. In this section we explain the framework, some of the abstractions we introduced (which model the properties from \S\ref{todo}), and how we can make a meaningful implementation of the build systems discussed in \S\ref{sec-background}.

\subsection{Framework}

As we saw in the introduction, a build system can be defined as:

\begin{minted}{haskell}
type Build c i k v = Compute c k v -> k -> Maybe i -> Map.Map k v -> (i, Map.Map k v)
\end{minted}

Using the framework we have built we can express the simplest and stupidest build system as:

\begin{minted}{haskell}
dumb :: Build Monad () k v
dumb compute = runM . f
    where f k = maybe (getStore k) (putStore k =<<) $ compute f k
\end{minted}

\begin{figure}
\begin{minted}{haskell}
data M i k v r
runM :: Default i => M i k v a -> Maybe i -> Map.Map k v -> (i, Map.Map k v)
getStore :: k -> M i k v v
putStore :: k -> v -> M i k v v
\end{minted}
Note: we have omitted the context on \textt{k}, things like \texttt{Ord} (so the implementation can use a finite map) or \texttt{Show} (so the implementation can produce nice error messages).
\caption{API with which to implement build systems}
\label{fig-M-api}
\end{figure}

The types of important definitions are given in Figure \ref{fig-M-api}

but
